% This file contains the abstract of the thesis

Blockchain has the power to revolutionize the public and private life of every individual. Bringing decentralization and transparency in an world of informational chaos is going to change the Internet and everything else with it. The strengths of this technology are immutability - no data corruption or lost, transparency - everyone has access to any exchange, decentralization - no central authority or single point of failure. In the business world Blockchain is creating new models of business from smart contracts to open networks enterprises for a wide range of industries from finance, sharing economy to solving the prosperity paradox by eliminating the global financial exclusion. Anyway, the adoption of Blockchain is a complex process so we don't expect to see major changes in the near future.

Soon after Blockchain's white paper publication, top digital companies had visualized its impact so they started investing in research programs and professionals for adopting this technology in their business. A multi-projects collaborative effort to speed this process is the Hyperledger which aim is to simplify the requirements of developing Blockchain based applications. We have identified a business area that can be improved within the IT department of Ixia - the CapEx business procedures and proposed a hardware supply-chain based on Blockchain using two of the Hyperledger projects: Fabric and Composer. \emph{\project} is a system that enables its participants to track every asset manufactured and used internally by the Keysight Technologies' employees.
