\chapter{Summary and Future Work}
\label{chapter:7}

This chapter summarizes our contributions to the Namecoin community and proposes future research directions. This paper put together all the knowledge acquired and systematized it in chapter~\ref{chapter:3}. 
At the end of this thesis we claim to achieve our objectives. We dedicated chapter~\ref{chapter:3} to the study of the Namecoin protocol filling the existing documentation gaps. In order to validate the naming information described in our study of the Namecoin protocol we build a tool that offers insights into the data stored in blockchain. The Namecoin Explorer tool performed well during our evaluation process by extracted naming data from blockchain and by filtering that information based on specific criteria. Using the tool's filtering feature we extracted naming services related information for evaluating the current state of the Namecoin system. In the end we offered a final forecast about the Namecoin system future based on trustworthy criteria.

There are still interesting Namecoin research directions that remained unexplored such as the geographic localization of top \code{.bit} domains (\code{google.bit}, \code{facebook.bit}, etc.). Determining the autonomous system (\code{AS}) of these domains, how top domains are distributed globally.
Using the results obtained in the evaluation phase and computing the \code{.bit} domain global distribution we aim to offer new analyses and forecasts. What are the security guarantees offered by DNS limitations, what are the financial perspectives of a company that choose to enter the Namecoin cryptocurrency market are only a few questions that we propose to answer in the future.


