\chapter{Introduction}
\label{chapter:intro}

\section{Project Description}
\label{sec:intro-section1}
The research report presents the actual state of Blockchain technology and business markets and identifies the fields that can benefit the most from the adoption of this technology in their current systems.

The report identifies all the areas that can make use of Blockchain by describing the existing system, the issues of it and how can Blockchain change and improve the users day-to-day activity. 
In order to be able to do such an analysis it's necessary to study the existing Blockchain businesses and their history from an idea to a successful startup.
After determining the keys elements that made these businesses so popular we focus our attention to Decision Support System architecture and the technical aspects of Blockchain so that we can have a strong view of this technology. Last but not least we describe the areas that are not using Blockchain technology but if they would adopt it they will improve massively their work flows.

\subsection{Project Scope}
\label{sub-sec:intro-subsection1}
This report aims to determine if it would be useful to create a Decision Support System that assists project managers to adopt Blockchain technology in the projects they conduct.
The DSS is going to be used in order to change the existing business system with a Blockchain solution that will simply the business processes and reduce the time of doing those activities.

\subsection{Project Objectives}
\label{sub-sec:intro-subsection2}
The list of objectives is the following:
\begin{itemize}
	\item \textbf{Explore Decision Support System for architectural solutions} is needed in order to determine what is the current state and if there are systems that offer technical solutions for improving or innovating complicated and old systems.
	\item \textbf{Understand Blockchain technology} is the next step that we need to accomplish in order to be able to develop a DSS that offers particular solution for a defined business.
	\item \textbf{Discover Blockchain successful businesses} helps detect the main elements that made these projects so popular. This step of market analysis is important in determining what are the target groups of these type of business, what is the size of a Blockchain business or what is the revenue of these startups in a certain period of time.
	\item \textbf{Determine the fields that could be innovated by the adoption of Blockchain} is the step when we identify the possible markets that would benefit from the DSS that we propose. Understanding their needs and limitations helps us offer the best version of a DSS.
\end{itemize}  

\subsection{Related Work}
\label{sub-sec:intro-subsection3}
This report focuses on the research work conduct during the first semester of master for determining if a DSS for Blockchain architectural solution is useful and is worth to develop.
The logical steps after selecting the research topics were to discover the existing DSS for architectural solutions, investigate the technical details of Blockchain, determine the main elements that made certain Blockchain businesses so successful and the possible fields where Blockchain can innovate.

Decision Support System is defined as "an extensible system, capable of ad-hoc analysis and
decision modeling, focused on future planning and used as unplanned and irregular timestamps"
accordingly to Moore and Chang \cite{def-dsss}. An important aspect of decision support systems is to
improve effectiveness, rather than the efficiency of decisions \cite{dds-efectiveness}.
A DSS that helps managers make decisions regarding the architectural solutions was proposed before. An example of such a system that decides between certain web framework is described in the article \cite{dss-web} but there is no DSS that offers solutions that uses Blockchain as a requirement for designing the project's architecture.

Before getting into the technical aspects of Blockchain is useful to investigate the impact of Blockchain on different areas of our life and the first step is to determine the areas that would benefit most from the Blockchain innovation.

In John Rampton's article \cite{5appforblock} are listed the five directions where the Blockchain technology could make a difference.
The Blockchain is closely linked with Bitcoin, a project published in 2009 by Satoshi Nakamoto as an alternative to traditional currency. The innovation brought by Bitcoin consists in the use of Blockchain as a storage for financial transactions in  a distributed system.
Since 2009, the Blockchain technology was used for different purposes and these are the five directions of innovation:
\begin{itemize}
	\item Smart Contracts are a concept introduced in the Ethereum project that allows applications to run as programmed without the possibility of downtime or fraud.
	\item Cloud Storage on Blockchain is a secure cloud storage solution that decreases the dependency of big market players such as Google or Amazon.
	\item Supply-Chain Communications and Proof-of-Provenance can benefit from Blockchain that offers the possibility to record digitally the state of a product along its chain to the final consumer.
	\item Paying Employees via digital assets reduces the time and money spent and is highly secured. The money have an unique identification(public key) and in each moment we can identify where they are in the network. The owner is the one that holds the private key.
	\item Electronic Voting using the consensus model of Blockchain is offering a solution to the voting manipulation issues and it protects all participants by assuring anonymity.
\end{itemize}