\chapter{Introduction}
\label{chapter:intro}

\section{Report Overview}
\label{sec:intro-section1}
The research report outlines the implementation details of a Blockchain business network modeling solution that aims to encourage non-technical people to adopt the Blockchain technology in their business or job.

Also the report argues the reasons of choosing this solution, the business motivation of it and what's our contribution to the Blockchain world.
In order to be able to understand these reasons it's important to have a clear view of the context and the existing open-source solutions in this area. 

Last but not least, we are going to present a complete use case of the application and how its output integrates with open-source solutions.

\subsection{Project Description}
\label{sub-sec:intro-subsection1}
\textbf{\project} is a generic business network modeling application that enables leaders and non-technical people to envision how Blockchain technologies will revolutionize the industry they activate in.

The business network is build accordingly to the Blockchain paradigm therefore the network is composed by three entities: participant, asset and transaction.

Another important aspect is that the application is going to work as an extension of Hyperledger Composer framework, therefore, the model format will be compatible with Hyperledger Composer Model Files.

\subsection{Project Objectives and Motivation}
\label{sub-sec:intro-subsection2}
Developing a Blockchain based application requires knowledge from different fields from networking, protocols, cryptography, encoding, digital signatures, algorithms, etc. Therefore, implementing a Blockchain system can be very complicated and complex even for experts and professionals in the field.
In addition, innovation is about building upon existing technologies and take advantage of the already knowledge of the communities so developing a Blockchain based solution from scratch is not necessary anymore. 
Another reason why business people and decision makers are skeptical is the fact that traditional Blockchain projects allows anyone to connect to the network and their identity cannot be verified. 

Starting from these perspectives, we have decided to implement an extension to a powerful framework developed by the Linux Foundation, Hyperledger Project.
Hyperledger Project is offering a solution to all the issues metionated above. The idea behind Hyperledger is to develop and nurture an ecosystem for the future of business blockchain technologies.
Hyperledger represents an alternative to the cryptocurrency-based blockchain model, and it offers blockchain frameworks and modules to support global enterprise solutions. The main focus of Hyperledger is to provide a transparent and collaborative approach for Blockchain development community.

Our Blockchain business network modeling application is fully compatible with the Hyperledger Composer framework and its main purpose is to help non-technical businessmen or other leaders to envision their work after adopting the Blockchain technology.
The idea of this application is the result of one year research work in the Blockchain world and it has arisen due to some difficulties encounter when testing the Hyperledger Composer framework.
We discovered that the Hyperledger Composer Framework has some limitations when it comes to creating the business network model and we want to fill in these gaps by developing an extension to this framework.
Therefore the solution proposed has the following objectives:
\begin{itemize}
	\item to offer the first modeling storage system of Blockchain business networks that doesn't require human technical assistance; 
	\item to get a fast sample of the business network from one of the areas where Blockchain will revolutionize the business flux;
	\item to reduce the time and costs of manually designing a Blockchain solution from scratch;
	\item to keep the compatibility with open-source projects that have the similar scope;
	\item to determine the fields that could be innovated by the adoption of Blockchain;
\end{itemize}  

By reaching these objectives, we will gone fill in the gaps of the Hyperledger Composer framework and we will provide a classification of business networks suitable for Blockchain by envisioning how IT\&C world will evolve. 

